# Data

## Description

## Missing value analysis

Import data:

```{r, include=FALSE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(redav)
options(warn = -1)
```

```{r}
raw_df = read_tsv('18k_Projects.csv', show_col_types = FALSE)
raw_df = raw_df %>% select(c(-Url, -`Start Timestamp (UTC)`, -`End Timestamp (UTC)`))

col_na = colSums(is.na(raw_df)) %>%
  sort(decreasing = TRUE)
col_na = col_na[col_na > 0]
col_na
```

The latitude and longitude have most missing values, following by creator website, Facebook friend number, creator's number of projects backed, number of videos in article and number of words in the "Risk and Challenges" section. It seems the missing value of (`Latitude`, `Longitude`) and (`# Videos`, `# Words (Risks and Challenges`) feature pairs appear at the same time.

To have a further look, we plot the missing value patterns:

```{r fig.width=8}
raw_df_miss = raw_df %>% 
  select (col_na %>% names())
names(raw_df_miss) = c('Lat.', 'Long.', 'Cre.Web.', 'FB.Con.', 'Cre.numB', 'num.Video', 'num.WoRC')

raw_df_miss %>% 
  plot_missing(percent = TRUE)
```

For features, there are around 50% of (`Latitude`, `Longitude`) pairs missing. `Creator Website` and `Facebook Connected` are also common missing values.

For data rows, most of them (around 25%) miss the `Facebook Connected` information only. It's reasonable for the missing values of creator's Facebook and creator's website, as they may not exist or are not shown on the crowd funding page.

We also identify several patterns:

First, the graph proves the assumption that (`Latitude`, `Longitude`) and (`# Videos`, `# Words (Risks and Challenges`) missing feature pairs appear at the same time. After a further inspect, we find it highly relevant with \`Location\`: The (`Latitude`, `Longitude`) is usually the same for a location. For spacial analysis purpose, we decide to use \`Location\` only.

Second, we find that the missing of `# Videos`, `# Words (Risks and Challenges` will appears together with \`Creator Website\`, `Latitude`, and `Longitude`. Such cases are rare, and only appears from January, 2014 to March, 2014. We checked the crowd funding webpages and found the data are accessible. Therefore, manually error or technical issue in data gathering may be the reason.

```{r}
#TODO
```

Thrid, `Facebook Friends` is missing if and only if `Facebook Connected` is `False`, which is reasonable.

```{r}
raw_df %>% filter(`Facebook Connected` == 'Yes' & is.na(`Facebook Friends`))
raw_df %>% filter(`Facebook Connected` == 'No' & (!is.na(`Facebook Friends`)))
```
