```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(redav)
```

```{r}
raw_df = read_tsv('18k_Projects.csv')
raw_df %>% head()
```

```{r}
# don't need:
# c(-Url, -`Start Timestamp (UTC)`, -`End Timestamp (UTC)`, -`Creator Bio`, -`Creator Website`)
# keep creator info for missing value analysis
raw_df = raw_df %>% select(c(-Url, -`Start Timestamp (UTC)`, -`End Timestamp (UTC)`))
raw_df %>% names()
```

Number of NAs in each columns

```{r}
col_na = colSums(is.na(raw_df)) %>%
  sort(decreasing = TRUE)
col_na = col_na[col_na > 0]
col_na
```

Spatial information loss is the most frequent. Also the Facebook information, the Creator's number of projects backed. Same for `#Videos` and \`#Words (Risks and Challenges)\`.

Heat maps:

```{r, fig.width=10}
raw_df_miss = raw_df %>% 
  select (col_na %>% names())
names(raw_df_miss) = raw_df_miss %>% names() %>% substr(1,8)

raw_df_miss %>% names()



raw_df_miss %>% 
  plot_missing(percent = TRUE)
```

Missing Patterns:

```{r}
raw_df %>% filter(is.na(`Creator - # Projects Backed`))
raw_df %>% filter(!is.na(`Facebook Friends`))
```

Guessing:

1.  creator project backed & date & project created

2.  note: has video means on the front page. \# video means inside the explanation text.

3.  facebook connected & facebook Friends: If no Facebook connected for the creator, then no information about their Facebook friends.

    ```{r}
    raw_df %>% filter(`Facebook Connected` == 'Yes' & is.na(`Facebook Friends`))
    raw_df %>% filter(`Facebook Connected` == 'No' & (!is.na(`Facebook Friends`)))
    # all return 0 lines
    ```

4.  #word/#video/creator website: 2014.1\~2014.3, maybe manually problem.

5.  issue: long/altti similar to location: redundancy
